IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-11 review/response_2.tex

\documentclass{article}

\usepackage[T1]{fontenc}
\usepackage[short]{optidef}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{xr-hyper}
\usepackage{hyperref}

\externaldocument[M-]{../submit_2}

\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}
\DeclareSIUnit{\belA}{BA}
\DeclareSIUnit{\dBA}{\deci\belA}

@@

\newenvironment{point}
	{\refstepcounter{point} \bigskip \noindent {\textbf{Comment~\thepoint} } ---\ \itshape}
	{\par}

\newenvironment{response}
	{\refstepcounter{response} \medskip \noindent \textbf{Response:}\ }
	{\medskip}

\begin{document}
	\includepdf{letter_2.pdf}

	\begin{editor}
		\begin{point}
			Please double-check Proposition~5 and the algorithm may not converge to a local optimal due to the coupling constraint~\eqref{M-co:original_rate}.
		\end{point}

@@

			For BCD Algorithm~\ref{M-al:bcd}, since Algorithm~\ref{M-al:gp} is involved per iteration, the computational complexity is exponential w.r.t. the number of subbands.
			\begin{framed}
				The steps are summarized in the BCD Algorithm~\ref{M-al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{M-al:gp}.
			\end{framed}

			For LC-BCD Algorithm~\ref{M-al:lc_bcd}, both waveform and active beamforming are obtained in closed form, and the computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
			\begin{framed}
				The computational complexity of Algorithm~\ref{M-al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{M-Luo2010}.
			\end{framed}
			\label{re:1.1}
		\end{response}

		\begin{point}
			Since this paper focused on IRS-aided SWIPT systems, it could be better if the authors can further enrich the survey part to make the paper more comprehensive. In particular, some papers have considered this kind of problem from a different aspect such as \cite{Xu2021}. It is kindly suggested to briefly discuss the main difference between \cite{Xu2021} and the problem considered in this paper.
		\end{point}

		\begin{response}
			Thank you for sharing this paper. Instead of optimizing the phase shift of each IRS element, it tailored a tile-based two-stage optimization framework for large-scale IRS to enable a flexible performance-complexity tradeoff. The model also adapts well to practical IRS models accounting AoA and AoD. We would like to kindly highlight that \cite{Xu2021} was not available at the time of submission of this manuscript. \cite{Xu2021} was indeed submitted in April 2021, i.e. several months after our submission to TCOM in Nov 2020. We therefore believe it is for authors of \cite{Xu2021} to further enrich the survey part of their manuscript by making it more comprehensive and discuss the difference between \cite{Xu2021} and this paper. Nevertheless to address the reviewer comments, we now compare with \cite{Xu2021c} which appeared on arXiv shortly before our submission.
			\begin{framed}
				Based on practical IRS and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage. The proposed framework provides a flexible tradeoff between performance and complexity. To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with co-located information decoder and energy harvester.
			\end{framed}
		\end{response}

@@

		\begin{point}
			It could be better if the authors can provide some references for the parameter values chosen in the simulation part.
		\end{point}

		\begin{response}
			The system layout follows \cite{M-Wu2019}. For the center frequency, we consider \SI{2.4}{\GHz} due to its ubiquitous and license-free properties. Note that the path loss can be greatly reduced (and the R-E performance can be improved) if the system operates at much lower frequency, as considered in most IRS papers. In the previous manuscript, we made a mistake in the choice of reference path loss. As indicated by Comment~\ref{pt:3.3}, even the free-space path loss should be around \SI{40}{\dB} at \SI{1}{\meter}. To fix this issue, we updated the path loss model as IEEE TGn channel model D that is representative of small environments such as residential homes and small offices \cite{M-Erceg2004}. It has three clusters with \SI{50}{\ns} r.m.s. delay spread, and the path loss exponent is \num{2} (i.e., free-space model) up to breakpoint distance \SI{10}{\meter} and \num{3.5} onwards to further penalize channels with large distance. We also raise the EIRP from \SI{36}{\dBm} to \SI{40}{\dBm} (which still complies with FCC regulations \cite{Afar2021}) and change the receive antenna gain from \SI{2}{\dBi} to \SI{3}{\dBi}. As for the rectenna parameters, the parameters are taken from \cite{M-Clerckx2016a} and the reference have been added to the revised manuscript.
		\end{response}

		\begin{point}
			The reviewer noticed that in Algorithm~\ref{M-al:lc_bcd}, there are two convergence criteria. It could be better if the authors can briefly interpret this issue.
		\end{point}

		\begin{response}
			We incorporated two cases (WIT/non-WIT) into Algorithm~\ref{M-al:lc_bcd}, where Algorithm~\ref{M-al:m_sca} is called during each iteration. To obtain the WIT point, the rate \eqref{M-eq:R_irs} instead of the DC \eqref{M-eq:z_irs_approx} should be maximized, such that the current expression is dropped and no SCA is involved. To clarify this point, we have updated the description on Algorithm~\ref{M-al:m_sca} as follows.
			\begin{framed}
				Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes. Specifically, the rate constraint \eqref{M-co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$. To achieve the WIT point ($\rho=0$), the rate \eqref{M-eq:R_irs} should be maximized, the current expression \eqref{M-eq:z_irs_approx} is not needed and no SCA is involved.
			\end{framed}
			Correspondingly, to achieve the WIT point, the LC-BCD Algorithm~\ref{M-al:lc_bcd} should maximizes $R$ instead of $z$. Line~\ref{li:convergence_begin}--\ref{li:convergence_end} was modified to avoid ambiguity and Algorithm~\ref{M-al:lc_bcd} is indexed below by \ref{al:lc_bcd} .
			\begin{algorithm}[!h]
				\caption{LC-BCD: Waveform and Beamforming.}
				\label{al:lc_bcd}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{M-eq:w}
					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{M-eq:R_waveform}, \eqref{M-eq:z_waveform}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{M-al:m_sca}
						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{M-eq:h_n}, \eqref{M-eq:b_n}
						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{M-eq:s_ip}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{M-eq:w}
						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{M-eq:R_waveform}, \eqref{M-eq:z_waveform}
						\If{$\rho=0$} \label{li:convergence_begin}
							\State $\Delta \gets  R^{(i)} - R^{(i-1)}$
						\Else
							\State $\Delta \gets  z^{(i)} - z^{(i-1)}$
						\EndIf
					\Until $\lvert \Delta \rvert \le \epsilon$ \label{li:convergence_end}
					\State Set $\boldsymbol{\phi}^{\star}\gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}\gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
				\end{algorithmic}
			\end{algorithm}
			The description on Algorithm~\ref{M-al:lc_bcd} have been updated as follows.
			\begin{framed}
				To achieve the WIT point ($\rho=0$), the rate \eqref{M-eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnotemark Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the LC-BCD algorithm obtains the R-E region by two-dimensional search over $\{\delta,\rho\}$ from \num{0} to \num{1}.
			\end{framed}
			\footnotetext{Recall in Remark~\ref{M-re:subband_tradeoff} that different subchannel designs lead to different capacities.}
			\label{re:1.4}
		\end{response}
	\end{reviewer}

@@

	\begin{reviewer}
		\begin{point}
			Although this paper reveals many useful insights, most of them are obtained via simulation and then explained via text. The overall theoretical contributions can be greatly improved if the authors can analytically verify or prove some of them, especially those unique to this paper. The authors may conduct the analysis under some simplified or special cases. If some of the observations and findings have been verified in existing papers, the authors can cite and echo these papers wherever necessary.
		\end{point}

		\begin{response}
			We believe the reviewer was referring to the array gain and scaling law suggested by Figs.~\ref{M-fi:scaling_tx} and \ref{M-fi:scaling_reflector}. Recall that $M$ refers to the number of transmit antenna, $N$ refers to the number of subbands, and $L$ refers to the number of IRS elements. From the perspective of WIT, coherent transmission achieves an array gain of $M$ \cite{M-Tse2005} and coherent reflection achieves an array gain of $L^2$ \cite{M-Wu2019}. From the perspective of WPT, \cite{M-Clerckx2016a} and \cite{M-Clerckx2018b} analytically proved the scaling law of the modulated and multisine waveforms. Even if a suboptimal waveform scheme (uniform power allocation in the frequency domain and matched filter in the spatial domain) is used, when $M$ is sufficiently large, the expectation of the DC scales quadratically with $M$. We have cited those papers in the revised manuscript.

			Next, we verify the last observation where the expectation of the DC scales quartically with $L$ in a much simplified scenario. Consider a SISO WPT system in a frequency-flat channel. We assume a sufficiently large $L$ such that the auxiliary link is dominant and the contribution of direct channel is omitted. With uniform power allocation to multisine ($s_{\mathrm{P},n} = \sqrt{2P}/\sqrt{N}$) in the frequency domain, the DC writes as
			\begin{equation}
				z_{\mathrm{UP}} = \beta_2 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^2 P + \frac{3}{8} \beta_4 (\Lambda_{\mathrm{I}} \Lambda_{\mathrm{R}} L \lvert X \rvert)^4 F,
			\end{equation}
			where $\beta_2$ and $\beta_4$ are fixed rectenna parameters, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$ are the path loss of incident and reflected links, $X$ is the random variable that models the small-scale double fading through one IRS element at any subband, and
			\begin{equation}
				F = \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} s_{n_1} s_{n_2} s_{n_3} s_{n_4} = \frac{4(2N^2+1)}{3N} P^2.
			\end{equation}
			Taking expectation over $\lvert X \rvert$, we have
			\begin{equation}
				\bar{z}_{\mathrm{UP}} = \beta_2 \Lambda_{\mathrm{I}}^2 \Lambda_{\mathrm{R}}^2 L^2 \mathbb{E}\{\lvert X \rvert^2\} P + \frac{3}{8} \beta_4 \Lambda_{\mathrm{I}}^4 \Lambda_{\mathrm{R}}^4 L^4 \mathbb{E}\{\lvert X \rvert^4\} \frac{2N^2+1}{2N} P^2,
			\end{equation}
			which verifies the scaling order of $L^4$. The analysis is not presented in the manuscript due to the space constraint.
		\end{response}

@@

		\begin{point}
			The authors are suggested to study the impact of IRS passive beamforming on the waveform design without IRS. For example, they can show the optimized waveforms with versus without IRS to unveil the interplay between them. Or even better, analytically compare the two waveforms.
		\end{point}

		\begin{response}
			Thank you for the suggestion. To see this, we first show one realization of direct channel amplitude (without IRS) and composite channel amplitude (with IRS) for WIT and WPT in Fig.~\ref{fi:channel_amplitude}. It is observed that under the configuration of choice, the WPT-optimized passive beamforming tends to concentrate the channel energy to relatively strong subbands, while the WIT-optimized passive beamforming achieves some balance among all subbands (similar to water-filling at high SNR).

			\begin{figure}[!h]
				\centering
				\resizebox{0.6\columnwidth}{!}{
					\includegraphics{../assets/channel_amplitude}
				}
				\caption{Sorted equivalent subchannel amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
				\label{fi:channel_amplitude}
			\end{figure}

@@

			On the other hand, the corresponding amplitude of modulated and multisine waveforms are shown in Fig.~\ref{fi:waveform_amplitude}. Note that no multisine is used for WIT and the case is not shown. It is observed that although passive beamforming can enable a flexible resource allocation opportunity at the channel (please refer to Response~\ref{re:2.10} for details), its impact on waveform design is unobvious.

			\begin{figure}[!h]
				\centering
				\subfloat[WIT waveform: modulated]{
				\resizebox{0.32\columnwidth}{!}{
						\input{../assets/waveform_wit_modulated.tex}
					}
				}
				\subfloat[WPT waveform: modulated]{
					\resizebox{0.32\columnwidth}{!}{
						\input{../assets/waveform_wpt_modulated.tex}
					}
				}
				\subfloat[WPT waveform: multisine]{
					\resizebox{0.32\columnwidth}{!}{
						\input{../assets/waveform_wpt_multisine.tex}
					}
				}
				\caption{Sorted modulated and multisine amplitude for WIT and WPT with and without IRS versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
				\label{fi:waveform_amplitude}
			\end{figure}

			We have modified the manuscript as follows to emphasize this point.
			\begin{framed}
				Fig.~6 reveals how IRS influences the (sorted) equivalent subchannel amplitude for one channel realization. Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for WIT and WPT are dissimilar. Under the specified configuration, the WPT-optimized IRS aligns the strong subbands to exploit the rectifier nonlinearity. On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large. This is reminiscent of the WF scheme at high SNR, but is realized by channel alignment instead of resource allocation. Nevertheless, the amplitude of modulated and multisine waveforms remains approximately unchanged when adding an IRS (the plots are not attached). In other words, IRS has a subtle impact on the waveform design.
			\end{framed}
			\label{re:2.2}
		\end{response}

@@

		\begin{point}
			In the low-complexity BCD, it is unclear how the authors dealt with the optimization of $\rho$ and $\delta$. In Algorithm~\ref{M-al:lc_bcd}, both of them are input. Did the authors perform a two-dimensional search here? Besides, they were assumed to be identical in the simulation. How will this assumption influence the performance loss?
		\end{point}

### 2021-08-12 assets/channel_amplitude.tex
:bento: Update assets

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,3.397in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00540099400856952\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS}

@@

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,2.663in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00314170999160457\\
2	0.00572485908105548\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00502314747430184\\
2	0.00698106265038798\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00330170889121358\\
2	0.00768466635770749\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,1.928in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=0.01,
ylabel style={font=\color{white!15!black}},
ylabel={Channel amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0016696476908254\\
2	0.00438348129943761\\
3	0.00457133324563245\\
4	0.00586320993785494\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00326549483873511\\
2	0.00557307586676685\\
3	0.00614450761039544\\
4	0.00726164815517615\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00166671759288851\\
2	0.0056728199729895\\
3	0.00568370327308551\\
4	0.00789867646413342\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,1.193in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00121164184157658\\
2	0.00238340383353008\\
3	0.00380683420957256\\
4	0.00397337725168322\\
5	0.00492524818026471\\
6	0.00528740868681232\\
7	0.00572071220385092\\
8	0.00587459497346489\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00264154779713112\\
2	0.00407667250014311\\
3	0.0049500895867949\\
4	0.00561010487339341\\
5	0.00637593781159189\\
6	0.0066081911104957\\
7	0.00719542472167268\\
8	0.00721447474714219\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00139675837927404\\
2	0.00297327122282322\\
3	0.00519768343232529\\
4	0.00524568965358895\\
5	0.00679027772006842\\
6	0.00680292145999757\\
7	0.00768611044981794\\
8	0.00771790378640739\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.457in,
at={(0.677in,0.458in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=0.01,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0011086419762005\\
2	0.00139817672195447\\
3	0.00200749223129634\\
4	0.00276896018192483\\
5	0.00348858569071252\\
6	0.00390863609607119\\
7	0.00410205684728188\\
8	0.00421746375099375\\
9	0.0046579451399174\\
10	0.00494987881895202\\
11	0.00517723522936086\\
12	0.00554845359626313\\
13	0.00558432983698075\\
14	0.00581133838542614\\
15	0.00582728083668895\\
16	0.00588378650142745\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00243240737767257\\
2	0.00291012490661641\\
3	0.00364483122694576\\
4	0.00450699183712641\\
5	0.00487492494056207\\
6	0.00519805292278296\\
7	0.00528263562038442\\
8	0.00589785004825321\\
9	0.0059831692545346\\
10	0.00639251285950617\\
11	0.00669911334288142\\
12	0.00680111371923813\\
13	0.00709923174422509\\
14	0.0071115147925566\\
15	0.00725582025143191\\
16	0.00726750007562416\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00123628236378877\\
2	0.00164057003125897\\
3	0.00244260991306404\\
4	0.00355854925167237\\
5	0.00469336613331463\\
6	0.00513906379517623\\
7	0.00552284927791181\\
8	0.00566659546513512\\
9	0.00636655282038687\\
10	0.0064643206674846\\
11	0.00710638804550398\\
12	0.00714275219594531\\
13	0.00755098826468563\\
14	0.00759919845334804\\
15	0.00776427719266845\\
16	0.00777739000911697\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,3.198in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=3, legend cell align=left, align=left, draw=white!15!black},
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00540099400856952\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS}

@@

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,2.513in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00314170999160457\\
2	0.00572485908105548\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00502314747430184\\
2	0.00698106265038798\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00330170889121358\\
2	0.00768466635770749\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.828in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
ylabel style={font=\color{white!15!black}},
ylabel={Channel amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0016696476908254\\
2	0.00438348129943761\\
3	0.00457133324563245\\
4	0.00586320993785494\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00326549483873511\\
2	0.00557307586676685\\
3	0.00614450761039544\\
4	0.00726164815517615\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00166671759288851\\
2	0.0056728199729895\\
3	0.00568370327308551\\
4	0.00789867646413342\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.143in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00121164184157658\\
2	0.00238340383353008\\
3	0.00380683420957256\\
4	0.00397337725168322\\
5	0.00492524818026471\\
6	0.00528740868681232\\
7	0.00572071220385092\\
8	0.00587459497346489\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00264154779713112\\
2	0.00407667250014311\\
3	0.0049500895867949\\
4	0.00561010487339341\\
5	0.00637593781159189\\
6	0.0066081911104957\\
7	0.00719542472167268\\
8	0.00721447474714219\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00139675837927404\\
2	0.00297327122282322\\
3	0.00519768343232529\\
4	0.00524568965358895\\
5	0.00679027772006842\\
6	0.00680292145999757\\
7	0.00768611044981794\\
8	0.00771790378640739\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,0.458in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0011086419762005\\
2	0.00139817672195447\\
3	0.00200749223129634\\
4	0.00276896018192483\\
5	0.00348858569071252\\
6	0.00390863609607119\\
7	0.00410205684728188\\
8	0.00421746375099375\\
9	0.0046579451399174\\
10	0.00494987881895202\\
11	0.00517723522936086\\
12	0.00554845359626313\\
13	0.00558432983698075\\
14	0.00581133838542614\\
15	0.00582728083668895\\
16	0.00588378650142745\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00243240737767257\\
2	0.00291012490661641\\
3	0.00364483122694576\\
4	0.00450699183712641\\
5	0.00487492494056207\\
6	0.00519805292278296\\
7	0.00528263562038442\\
8	0.00589785004825321\\
9	0.0059831692545346\\
10	0.00639251285950617\\
11	0.00669911334288142\\
12	0.00680111371923813\\
13	0.00709923174422509\\
14	0.0071115147925566\\
15	0.00725582025143191\\
16	0.00726750007562416\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00123628236378877\\
2	0.00164057003125897\\
3	0.00244260991306404\\
4	0.00355854925167237\\
5	0.00469336613331463\\
6	0.00513906379517623\\
7	0.00552284927791181\\
8	0.00566659546513512\\
9	0.00636655282038687\\
10	0.0064643206674846\\
11	0.00710638804550398\\
12	0.00714275219594531\\
13	0.00755098826468563\\
14	0.00759919845334804\\
15	0.00776427719266845\\
16	0.00777739000911697\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%
